```{r}
#| label: setup
#| include: false
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  fig.align = "center",
  out.width = "100%"
)

library(countdown)

# Load required packages for QR code generation
if (!require("qrcode")) install.packages("qrcode")
library(qrcode)

if (!require("magrittr")) install.packages("magrittr")
library(magrittr)

if (!require("here")) install.packages("here")
library(here)
here::i_am("Presentation/presentation.qmd")

include_local_figure <- function(data_source) {
  knitr::include_graphics(
    path = here::here(
      "Presentation/Materials",
      data_source
    ),
    error = TRUE
  )
}

source(
  here::here("R/set_r_theme.R")
)

# Dynamic project name generation using {here}
project_name <- 
  basename(here::here())

# Create a cleaner display name for the lecture
display_name <- 
  gsub("SSoQE-", "", project_name) %>%
  gsub("_", " ", .) %>%
  tools::toTitleCase()

# Create dynamic URLs
github_url <- 
  paste0(
    "https://github.com/SSoQE/",
     project_name
  )

slides_url <- 
  paste0(
    "https://ssoqe.github.io/", 
    project_name, "/"
  )
```

# {.title}

<br>

:::: {.columns}

::: {.column width="80%"}
:::

::: {.column width="20%"}

```{r}
#| label: ssoqe-logo-title
include_local_figure("Logos/SSOQE_logo3.png")
```

:::

::::

:::: {.r-hstack}
::: {data-id="box1" style="background: `r ssoqe_cols['black']`; width: 135px; height: 15px; margin: 0px;"}
:::

::: {data-id="box2" style="background: `r ssoqe_cols['cambridge_blue']`; width: 405px; height: 15px; margin: 0px;"}
:::

::: {data-id="box3" style="background: `r ssoqe_cols['persian_green']`; width: 225px; height: 15px; margin: 0px;"}
:::

::: {data-id="box4" style="background: `r ssoqe_cols['satin_sheen_gold']`; width: 135px; height: 15px; margin: 0px;"}
:::
::::

::: {.text-color-white .text-font-heading .text-size-heading2 .text-bold}
`r display_name`
:::

:::: {.columns}

::: {.column width="20%"}

:::

::: {.column width="80%" .text-right .text-size-body}
[👤]()Author name

[Science School of Quantitative Ecology 2025]{.text-color-black}

[bit.ly/SSoQE](https://bit.ly/SSoQE){.text-color-black}
:::

::::


## [This presentation]{.text-bold .r-fit-text} {.title}

:::: {.columns}

::: {.column width="70%"}
::: {.r-fit-text}
[😸 Code on GitHub](`r github_url`)

[🖥️ Slides](`r slides_url`)

[![](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
:::
:::

::: {.column width="30%"}
```{r}
#| label: qr_slides
qr_slides <-
  qrcode::qr_code(
    slides_url,
    ecl = "H"
  )

qrcode::generate_svg(
  qrcode = qr_slides,
  filename = here::here("Presentation/Materials/QR/qr_slides.svg"),
  foreground = ssoqe_cols['white'],
  background = ssoqe_cols['midnight_green']
)

include_local_figure("QR/qr_slides.svg")
```
:::

::::

# [Outro]{.bold .r-fit-text} {.title}

## SPROuT

The materials used in this presentation are further expanded in a greater detail in course [Science Powered through Reproducibility, Openness, and Teamwork (SPRouT)](https://github.com/CUNI-SPRouT) taught at Charles University.

```{r}
#| label: sprot-logo
include_local_figure("Logos/sprout_logo.png")
```

## About me

:::: {.columns}

::: {.column width="25%"}
```{r}
#| label: personal sticker
include_local_figure("Author/Ondrej_Mottl-transparent-shadow.png")
```

```{r}
#| label: linktree QR
qr_personal_web <-
  qrcode::qr_code(
    "https://bit.ly/ondrej_mottl",
    ecl = "H"
  )

qrcode::generate_svg(
  qrcode = qr_personal_web,
  filename = here::here("Presentation/Materials/QR/qr_personal_web.svg"),
  foreground = ssoqe_cols['black'],
  background = ssoqe_cols['white']
)

include_local_figure("QR/qr_personal_web.svg")
```
:::

::: {.column width="5%"}
:::

::: {.column width="70%"}
[Ondřej Mottl]{.bold .r-fit-text .text-color-black}
Assistant Professor at [Charles University](https://cuni.cz/UK-1.html)

Head of the 🧑‍💻 [Laboratory of Quantitative Ecology](https://ondrejmottl.github.io/lab/about_the_lab.html)

* 📧 Ondrej.mottl(at)gmail.com
* 🦋 [ondrejmottl.bsky.social](https://bsky.app/profile/ondrejmottl.bsky.social)
* 🐱 [Github](https://github.com/OndrejMottl)
* 🆔 [ORCID](https://orcid.org/0000-0002-9796-5081)
* 🌐 [Personal webpage](https://ondrejmottl.github.io/)
:::

::::
